Model-based Reinforcement Learning with Fast Posterior Updates

### 2023-03-24 paper/main.tex
added citations
added proog
updated abstract after meeting 23rd march

\begin{abstract}
  % Reinforcement learning (RL) agents typically do not utilise the information previously gained during an episode.
  % as they perform learning offline, i.e. after an episode.
  % Reinforcement learning (RL) agents typically perform learning after an episode, ignoring the potential information gain whilst collecting data.
  Reinforcement learning (RL) agents typically perform learning offline and do not utilise the information gained during an episode.
  We present a Bayesian model-based RL algorithm which incorporates this information by updating a dynamic model's posterior during an episode.
  Our method leverages the fast posterior updates available in the dual parameterisation of sparse variational Gaussian processes.
  Importantly, our algorithm scales to 1) environment's with high dimensional state-spaces as it is built upon the connection between Bayesian neural networks (BNNs) and
  Gaussian processes (GPs) and 2) long episodes, as the complexity of our updates is independent of episode length.
  We demonstrate that our fast posterior updates improve sample efficiency in environments with action penalties, a notoriously difficult
  challenge for model-based RL algorithms.
\end{abstract}

@@

\subsection{Efficiently Sampling Functions for Posterior Sampling}
\cite{wilsonEfficiently2020}

@@

>>>>

\begin{abstract}
  % Reinforcement learning (RL) agents typically do not utilise the information previously gained during an episode.
  % as they perform learning offline, i.e. after an episode.
  % Reinforcement learning (RL) agents typically perform learning after an episode, ignoring the potential information gain whilst collecting data.
  % Reinforcement learning (RL) agents typically perform learning offline and do not utilise the information gained during an episode.
  % We present a Bayesian model-based RL algorithm which incorporates this information by updating a dynamic model's posterior during an episode.
  % Our method leverages the fast posterior updates available in the dual parameterisation of sparse variational Gaussian processes.
  % Importantly, our algorithm scales to 1) environment's with high dimensional state-spaces as it is built upon the connection between Bayesian neural networks (BNNs) and
  % Gaussian processes (GPs) and 2) long episodes, as the complexity of our updates is independent of episode length.
  % We demonstrate that our fast posterior updates improve sample efficiency in environments with action penalties, a notoriously difficult
  % challenge for model-based RL algorithms.
  Reinforcement learning (RL) agents typically perform learning offline and do not utilise the information gained during an episode.
  We present a Bayesian model-based RL algorithm which incorporates this information by updating a dynamic model's posterior during an episode.
  Typically training a neural network dynamic model is not feasible and nonparameteric methods such as Gaussian processes scale poorly with data.
  Importantly, our algorithm scales to 1) environment's with high dimensional state-spaces, 2) large data sets and 3) long episodes,
  as the complexity of our updates is independent of episode length.
  We demonstrate that our fast posterior updates improve sample efficiency in environments with action penalties, a notoriously difficult
  challenge for model-based RL algorithms.
\end{abstract}

@@

\cite{rossellApproximateLaplaceApproximations2021}

\subsection{Efficiently Sampling Functions for Posterior Sampling}
\cite{wilsonEfficiently2020}
\cite{wilsonPathwise2021}

@@

\input{proof.tex}
